\chapter{APPENDIX}

\section{Minimum Software Requirements}
\medskip
\textbf{Operating System}: Windows 10/11, macOS, or Linux (Ubuntu/Debian recommended for server environments)
\\\\
\textbf{Development Environment}: XAMPP, WAMP, Laravel Herd, or Laravel Sail (Docker) for local hosting and database management.
\\\\
\textbf{Web Server}: Apache or Nginx
\\\\
\textbf{Database Engine}: MySQL 8.0+ or MariaDB 10.3+
\\\\
\textbf{Programming Languages / Frameworks}: 
\begin{itemize}
    \item PHP 8.2 or higher
    \item Laravel 11 Framework
    \item Node.js (v18+) and NPM (for compiling frontend assets)
    \item Tailwind CSS (via Vite)
\end{itemize}
\textbf{Web Browser}: Google Chrome, Mozilla Firefox, Apple Safari, or Microsoft Edge (Latest versions recommended for optimal UI rendering).

\section{Minimum Hardware Requirements}
\textbf{Processor}: Intel Core i3 (or AMD Ryzen 3 equivalent) or higher to efficiently run a local development server and process PHP scripts.
\\\\
\textbf{RAM}: 4 GB (8 GB recommended for smoother performance when running Node.js build tools and the database concurrently).
\\\\
\textbf{Graphics Card}: Integrated graphics are sufficient; no dedicated GPU is required as this is a server-rendered web application.
\\\\
\textbf{Storage}: Minimum 1 GB of free space for the application files, vendor dependencies (Composer/NPM), and the local database. An SSD is recommended for faster read/write operations during development.
\\\\
\textbf{Display}: A monitor with at least 1366x768 resolution for clear visibility of the dashboard and data tables.
\\\\
\textbf{Input Devices}: Standard keyboard and mouse for navigation and data entry.
\\\\
\textbf{Network Connectivity}: An active internet connection is required initially to download Composer packages and NPM dependencies, though the application can be run locally (offline) on `localhost` once set up.
